Human judgement forecasting of COVID-19 in the UK

### 2023-05-08 manuscript/manuscript.tex
small corrections to WIS

The WIS is a strictly proper scoring rule yielding non-negative values, with smaller values implying better performance. A forecaster, in expectation, optimises their score by providing a predictive distribution $F$ that is equal to the data-generating distribution $G$, and is therefore incentivised to report their true belief. The WIS can be understood as an approximation of the continuous ranked probability score (CRPS) for forecasts in a quantile-based format, which itself represents a generalisation of the absolute error to predictive distributions. The WIS can be decomposed into three separate penalty components: forecast dispersion (i.e., uncertainty of forecasts), overprediction and underprediction.

>>>>

The WIS is a proper scoring rule yielding non-negative values, with smaller values implying better performance. A forecaster, in expectation, optimises their score by providing a predictive distribution $F$ that is equal to the data-generating distribution $G$, and is therefore incentivised to report their true belief. The WIS can be understood as an approximation of the continuous ranked probability score (CRPS, \citealt{gneitingProbabilisticForecastsCalibration2007}) for forecasts in a quantile-based format. The CRPS, in turn, represents a generalisation of the absolute error to predictive distributions. The WIS can be decomposed into three separate penalty components (corresponding to the three terms in the definition of the interval score): forecast dispersion (i.e., uncertainty of forecasts), overprediction and underprediction.
